Vitis acerifolia LM

### 2018-12-04 V_acerifolia_LM.Rmd
Interpret LM

We ran a LM for leaf number and total teeth.
```{r}
ac_tt_lm <- lm(avg.tt ~ leaf, data = ac_l_means)
summary(ac_tt_lm)
```

@@

We wanted to test leaf number and feret diameter ratio.
```{r}
skim(acerifolia, total.teeth)
ac_fdr_plot <- ggplot(acerifolia, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_fdr_plot <- ac_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
ac_fdr_plot

@@

We ran a LM for leaf number and feret diamter ratio.
```{r}
ac_fdr_lm <- lm(avg.fdr ~ leaf, data = ac_l_means)
summary(ac_fdr_lm)
```

@@

We tested leaf number and tooth area:perimeter.
```{r}
skim(acerifolia, tooth.area.perimeter)
ac_tap_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_tap_plot <- ac_tap_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
ac_tap_plot

@@

@@

We tested leaf number and tooth area:internal perimeter.
```{r}
skim(acerifolia, tooth.area.int.perimeter)
ac_taip_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_taip_plot <- ac_taip_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
ac_taip_plot

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

```{r}
ac_taba15_seg <- segmented(ac_taba15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(ac_taba15_seg)
```

>>>>

We ran a LM for leaf number and total teeth.
```{r}
ac_tt_lm <- lm(avg.tt ~ leaf, data = ac_l_means)
summary(ac_tt_lm)
ac_tt_res <- resid(ac_tt_lm)
plot(avg.tt ~leaf, ac_l_means,
     ylab="Residuals", xlab="leaf",
     main="Total teeth")
```
The average leaf in the dataset has 47 teeth and the number of teeth decreases by one as leaves get older. There is a relationship between leaf number and total teeth and about half of the variance in total teeth can be explained by leaf number.

@@

We wanted to test leaf number and feret diameter ratio.
```{r}
skim(acerifolia, total.teeth)
ac_fdr_plot <- ggplot(acerifolia, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_fdr_plot <- ac_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
ac_fdr_plot
```

@@

We ran a LM for leaf number and feret diamter ratio.
```{r}
ac_fdr_lm <- lm(avg.fdr ~ leaf, data = ac_l_means)
summary(ac_fdr_lm)
```
The average leaf in the dataset has an FDR of 0.7 and the FDR increases by ~0.009 as the leaves get older. There is a relationship between leaf number and FDR and about 75% of the variance in FDR can be explained by leaf number.

@@

We tested leaf number and tooth area:perimeter.
```{r}
skim(acerifolia, tooth.area.perimeter)
ac_tap_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_tap_plot <- ac_tap_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
ac_tap_plot
```

@@

The average leaf in the dataset has a TAP of 0.04 and the TAP increases by 0.003 as the leaves get older. There is a relationship between leaf number and TAP and about 34% of the variance in TAP can be explained by leaf number.

@@

We tested leaf number and tooth area:internal perimeter.
```{r}
skim(acerifolia, tooth.area.int.perimeter)
ac_taip_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_taip_plot <- ac_taip_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
ac_taip_plot
```

@@

The average leaf in the dataset has a TAIP of 0.06 and the TAIP increases by 0.003 as the leaves get older. There is not a strong relationship between leaf number and TAIP and about 22% of the variance in TAP can be explained by leaf number.

@@

The average leaf in the dataset has a ATA of 0.05 and the TAIP increases by 0.007 as the leaves get older. There is a weak relationship between leaf number and ATA and about 32% of the variance in ATA can be explained by leaf number.

@@

The average leaf in the dataset has a TP of 1.12 and the TP decreases by 0.04 as the leaves get older. There is a relationship between leaf number and TP and about 30% of the variance in TP can be explained by leaf number.

@@

The average leaf in the dataset has a TIP of 1.67 and the TIP decreases by 0.07 as the leaves get older. There is a relationship between leaf number and TIP and about 45% of the variance in TIP can be explained by leaf number.

@@

The average leaf in the dataset has a PA of 2.33 and the PA decreases by 0.14 as the leaves get older. There is a relationship between leaf number and PA and about 41% of the variance in PA can be explained by leaf number.

@@

The average leaf in the dataset has a PR of 1.5 and the PR decreases by 0.02 as the leaves get older. There is a relationship between leaf number and PR and about 68% of the variance in PR can be explained by leaf number.

@@

The average leaf in the dataset has a CP of 92 and the CP decreases by 4.3 as the leaves get older. There is a strong relationship between leaf number and CP and about 75% of the variance in PR can be explained by leaf number.

@@

The average leaf in the dataset has a SF of 0.12 and the SF increases by 0.01 as the leaves get older. There is a strong relationship between leaf number and SF and about 95% of the variance in SF can be explained by leaf number.

@@

The average leaf in the dataset has a TBA of 2.98 and the TBA decreases by 0.23 as the leaves get older. There is a strong relationship between leaf number and TBA and about 40% of the variance in TBA can be explained by leaf number.

@@

The average leaf in the dataset has a TABA of 0.069 and the TABA decreases by 0.0038 as the leaves get older. There is not a relationship between leaf number and TABA and about 0% of the variance in TBA can be explained by leaf number.

@@

The average leaf in the dataset has a TABA of 0.081 and the TABA decreases by 0.0014 as the leaves get older. There is a weak relationship between leaf number and TABA and about 0% of the variance in TBA can be explained by leaf number.

```{r}
ac_taba15_seg <- segmented(ac_taba15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(5, 7, 10)))
summary(ac_taba15_seg)
```
